Bayesian Sparsification of $\cplx$-valued networks

### 2020-01-30 paper/paper.tex
added some additional plans and fleshed out a conclusion

% a copule of plot form mnist and fashion mnist
% discuss the plots describing how the test -perfromance grows with compression
% hinting at overfitting/regularization effects of masking and sparsification

@@

\subsection{Tasks and datasets} % (fold)
\label{sub:tasks_and_datasets}

\citet{trabelsi_deep_2017} study the applicability of $\cplx$-valued networks to image
classification (CIFAR-10, CIFAR-100, reduced train of SVHN), music-transcription
(MusicNet), and Speech Spectrum prediction (TIMIT).

% complex high-dimensional time series In-phase Quadrature (IQ)

\citep{monning_evaluation_2018}
\citep{jankowski_complex-valued_1996}
\citep{amin_complex-valued_2012}
\citep{sarroff_complex_2018}

% subsection tasks_and_datasets (end)

@@

>>>>

% a couple of plots from MNIST and Fashion-MNIST
% write a note on the incompressible parameters (bias, batch norm etc.)
% discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
% hinting at overfitting/regularization effects of masking and sparsification

@@

\subsection{CIFAR10/100} % (fold)
\label{sub:cifar10_100}

% mention the same experimental setup as in MNIST
% describe the VGG16 model and its cplx-valued modification
% mention that fourier-features perfomed worse than raw image data embeded in to $\cplx$
% compare compressed cplx-vgg against real-vgg
% draw some conclusions

% subsection cifar10_100 (end)

\subsection{MusciNet} % (fold)
\label{sub:muscinet}

\citet{trabelsi_deep_2017} designed a complex-valued network that achieved SOTA results
on the music-transcription task on MusicNet, \citep{thickstun_learning_2017}.

% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017

% mention 44khz to 11khz downsampling and the extraction of the originally recommended test set
% and the validation set chosen by Trabelsi et al.

% Describe the network by Trabelsi and then present the reslts form then model with kernel size \textbf{6} 
% the causally mantion that you also conducted a large study of an inferior model with kenrel size 3.
% (do not mention that this was a mistake, you dummy!)

% subsection muscinet (end)

@@

Despite having higher arithmetic complexity, complex-valued models provide built-in
joint amplitude-phase transformations and regularization, \citep{hirose_complex-valued_2009},
and enjoy superior performance on naturally $\cplx$-valued datasets \citep{citation_needed},
that occur in ultra high-frequency radio communications and audio signal processing. In this
study we address the issue of excessive the arithmetic complexity of complex-valued networks
by extending the existing Bayesian compression techniques by \citet{kingma_variational_2015},
\citet{molchanov_variational_2017} and \citet{kharitonov_variational_2018} to $\cplx$-valued
model parameters. To this end we have conducted a large scale numerical study of such networks
to assess the performance-compression rate trade-off and achieved performance, comparable
to SOTA on the MusicNet dataset.

Much like $\real$-valued variational dropout, the proposed $\cplx$-valued extension can be
straightforwardly enhanced to provide structured sparsity. The results of this study have
direct implications for real-time signal processing with embedded deep learning applications
both in terms of lower storage requirements and higher throughput stemming from fewer
floating-point multiplications.
